---
title: "Not So Dumb Diary"
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
    social: menu
    theme: paper
    source_code: embed
    vertical_layout: fill
    runtime: shiny
---

<style>                     
.navbar {
  background-color:black;
  hover-color:yellow;
}

</style> 



```{r setup, include=FALSE}
library(flexdashboard)
library(shiny)
library(knitr)
library("tm")
library("SnowballC")
library("wordcloud")
library("wordcloud2")
library("RColorBrewer")
library("syuzhet")
library(ggplot2)
library(dslabs)
library(imager)
library(ngram)
library(tableHTML)
```
<html>
  <head>
    <meta charset="utf-8">
    <style>
html {
  height:100%;
}

body {
  margin:0;
}

.bg {
  animation:slide 3s ease-in-out infinite alternate;
  background-image: linear-gradient(-60deg, #d4f4fd 50%, #feeaf9 50%, #fddff3 50%);
  bottom:0;
  left:-50%;
  opacity:.5;
  position:fixed;
  right:-50%;
  top:0;
  z-index:-1;
}

.bg2 {
  animation-direction:alternate-reverse;
  animation-duration:4s;
}

.bg3 {
  animation-duration:5s;
}

.content {
  background-color:rgba(255,255,255,.8);
  border-radius:.25em;
  box-shadow:0 0 .25em rgba(0,0,0,.25);
  box-sizing:border-box;
  left:50%;
  padding:10vmin;
  position:fixed;
  text-align:center;
  top:50%;
  transform:translate(-50%, -50%);
}

h1 {
  font-family:monospace;
}

@keyframes slide {
  0% {
    transform:translateX(-25%);
  }
  100% {
    transform:translateX(25%);
  }
}



Resources1× 0.5× 0.25×Rerun
    </style>
   
    <title>Document</title>
  </head>
  <body>
<div class="bg"></div>
<div class="bg bg2"></div>
<div class="bg bg3"></div>

  </body>
</html>


Upload Your Diary
=====================================================================



row {data-width=650}
----------------------------------------------------------------------
### Date
```{r}
valueBox(value=Sys.Date(),icon="fa-calendar")

```

### Time
```{r}
valueBox(value=format(Sys.time(),"%X"),icon="fa-clock")

```

### Time Zone
```{r}
#textOutput("len")
temp <- Sys.timezone()
valueBox(value=temp,icon="fa-globe")

```


Column {data-width=250}
----------------------------------------------------------------------



```{r}

                                    fileInput('file1', 'Upload your Diary',
                accept=c('text/csv', 
                         'text/comma-separated-values,text/plain', 
                         '.csv','.tsv'))
 
   
tags$style("
             .btn-file {  
             background-color:black; 
             border-color: grey;
             color:white;
             
             }

             ")

 tableOutput("contents")
 
  

```

Column {data-width=250}
----------------------------------------------------------------------


```{r}

output$contents <- renderTable({

        
        # input$file1 will be NULL initially. After the user selects
        # and uploads a file, head of that data file by default,
        # or all rows if selected, will be shown.
        
        req(input$file1)
        
        text <- readLines(input$file1$datapath)
        # Load the data as a corpus
        TextDoc <- Corpus(VectorSource(text))
        
        #Replacing "/", "@" and "|" with space
        toSpace <- content_transformer(function (x , pattern ) gsub(pattern, " ", x))
        TextDoc <- tm_map(TextDoc, toSpace, "/")
        TextDoc <- tm_map(TextDoc, toSpace, "@")
        TextDoc <- tm_map(TextDoc, toSpace, "\\|")
        # Convert the text to lower case
        TextDoc <- tm_map(TextDoc, content_transformer(tolower))
        # Remove numbers
        TextDoc <- tm_map(TextDoc, removeNumbers)
        # Remove english common stopwords
        TextDoc <- tm_map(TextDoc, removeWords, stopwords("english"))
        # Remove your own stop word
        # specify your custom stopwords as a character vector
        TextDoc <- tm_map(TextDoc, removeWords, c("s", "company", "team")) 
        # Remove punctuations
        TextDoc <- tm_map(TextDoc, removePunctuation)
        # Eliminate extra white spaces
        TextDoc <- tm_map(TextDoc, stripWhitespace)
        # Text stemming - which reduces words to their root form
        TextDoc <- tm_map(TextDoc, stemDocument)
        
        # Build a term-document matrix
        TextDoc_dtm <- TermDocumentMatrix(TextDoc)
        dtm_m <- as.matrix(TextDoc_dtm)
        # Sort by descearing value of frequency
        dtm_v <- sort(rowSums(dtm_m),decreasing=TRUE)
        dtm_d <- data.frame(word = names(dtm_v),freq=dtm_v)
        # Display the top 5 most frequent words
        #head(dtm_d, 5)
        
        return(text)
        
        
    })

    
```

Analysis
===============================
Column {data-width=350}
-----------------------------------------------------------------------

### Top 5 Most Frequently Used Words

```{r}
plotOutput("FrequentWords")
output$FrequentWords <- renderPlot({
        
        # input$file1 will be NULL initially. After the user selects
        # and uploads a file, head of that data file by default,
        # or all rows if selected, will be shown.
        
        req(input$file1)
        
        text <- readLines(input$file1$datapath)
        # Load the data as a corpus
        TextDoc <- Corpus(VectorSource(text))
        
        #Replacing "/", "@" and "|" with space
        toSpace <- content_transformer(function (x , pattern ) gsub(pattern, " ", x))
        TextDoc <- tm_map(TextDoc, toSpace, "/")
        TextDoc <- tm_map(TextDoc, toSpace, "@")
        TextDoc <- tm_map(TextDoc, toSpace, "\\|")
        # Convert the text to lower case
        TextDoc <- tm_map(TextDoc, content_transformer(tolower))
        # Remove numbers
        TextDoc <- tm_map(TextDoc, removeNumbers)
        # Remove english common stopwords
        TextDoc <- tm_map(TextDoc, removeWords, stopwords("english"))
        # Remove your own stop word
        # specify your custom stopwords as a character vector
        TextDoc <- tm_map(TextDoc, removeWords, c("s", "company", "team")) 
        # Remove punctuations
        TextDoc <- tm_map(TextDoc, removePunctuation)
        # Eliminate extra white spaces
        TextDoc <- tm_map(TextDoc, stripWhitespace)
        # Text stemming - which reduces words to their root form
        TextDoc <- tm_map(TextDoc, stemDocument)
        
        # Build a term-document matrix
        TextDoc_dtm <- TermDocumentMatrix(TextDoc)
        dtm_m <- as.matrix(TextDoc_dtm)
        # Sort by descearing value of frequency
        dtm_v <- sort(rowSums(dtm_m),decreasing=TRUE)
        dtm_d <- data.frame(word = names(dtm_v),freq=dtm_v)
        # Display the top 5 most frequent words
        head(dtm_d, 5)
        
        return(barplot(dtm_d$freq, las = 2, names.arg = dtm_d$word,
        col ="lightgreen", main ="Top 5 most frequent words",
        ylab = "Word frequencies"))
})
```

### Pie Chart

```{r}
plotOutput("density")
output$density <- renderPlot({
        
        # input$file1 will be NULL initially. After the user selects
        # and uploads a file, head of that data file by default,
        # or all rows if selected, will be shown.
        
        req(input$file1)
        
        text <- readLines(input$file1$datapath)
        # Load the data as a corpus
        TextDoc <- Corpus(VectorSource(text))
        
        #Replacing "/", "@" and "|" with space
        toSpace <- content_transformer(function (x , pattern ) gsub(pattern, " ", x))
        TextDoc <- tm_map(TextDoc, toSpace, "/")
        TextDoc <- tm_map(TextDoc, toSpace, "@")
        TextDoc <- tm_map(TextDoc, toSpace, "\\|")
        # Convert the text to lower case
        TextDoc <- tm_map(TextDoc, content_transformer(tolower))
        # Remove numbers
        TextDoc <- tm_map(TextDoc, removeNumbers)
        # Remove english common stopwords
        TextDoc <- tm_map(TextDoc, removeWords, stopwords("english"))
        # Remove your own stop word
        # specify your custom stopwords as a character vector
        TextDoc <- tm_map(TextDoc, removeWords, c("s", "company", "team")) 
        # Remove punctuations
        TextDoc <- tm_map(TextDoc, removePunctuation)
        # Eliminate extra white spaces
        TextDoc <- tm_map(TextDoc, stripWhitespace)
        # Text stemming - which reduces words to their root form
        TextDoc <- tm_map(TextDoc, stemDocument)
        
        # Build a term-document matrix
        TextDoc_dtm <- TermDocumentMatrix(TextDoc)
        dtm_m <- as.matrix(TextDoc_dtm)
        # Sort by descearing value of frequency
        dtm_v <- sort(rowSums(dtm_m),decreasing=TRUE)
        dtm_d <- data.frame(word = names(dtm_v),freq=dtm_v)
        syuzhet_vector <- get_sentiment(text, method="syuzhet")
# see the first row of the vector
head(syuzhet_vector)
# see summary statistics of the vector
summary(syuzhet_vector)
d<-get_nrc_sentiment(text)
# head(d,10) - to see top 10 lines of the get_nrc_sentiment dataframe
head(d,10)
td<-data.frame(t(d))
#The function rowSums computes column sums across rows for each level of a grouping variable.
td_new <- data.frame(rowSums(td))
#Transformation and cleaning
names(td_new)[1] <- "count"
td_new <- cbind("sentiment" = rownames(td_new), td_new)
rownames(td_new) <- NULL
td_new2<-td_new[1:8,]

        # Display the top 5 most frequent words
        return(ggplot(td_new2, aes(x="", y=sentiment, fill=sentiment)) +geom_bar(stat="identity", width=1) +
  coord_polar("y", start=0)+theme_void() 
)
})

```


### Word Cloud

```{r}
plotOutput("cloud")
output$cloud <- renderPlot({
        
        # input$file1 will be NULL initially. After the user selects
        # and uploads a file, head of that data file by default,
        # or all rows if selected, will be shown.
        
        req(input$file1)
        
        text <- readLines(input$file1$datapath)
        # Load the data as a corpus
        TextDoc <- Corpus(VectorSource(text))
        
        #Replacing "/", "@" and "|" with space
        toSpace <- content_transformer(function (x , pattern ) gsub(pattern, " ", x))
        TextDoc <- tm_map(TextDoc, toSpace, "/")
        TextDoc <- tm_map(TextDoc, toSpace, "@")
        TextDoc <- tm_map(TextDoc, toSpace, "\\|")
        # Convert the text to lower case
        TextDoc <- tm_map(TextDoc, content_transformer(tolower))
        # Remove numbers
        TextDoc <- tm_map(TextDoc, removeNumbers)
        # Remove english common stopwords
        TextDoc <- tm_map(TextDoc, removeWords, stopwords("english"))
        # Remove your own stop word
        # specify your custom stopwords as a character vector
        TextDoc <- tm_map(TextDoc, removeWords, c("s", "company", "team")) 
        # Remove punctuations
        TextDoc <- tm_map(TextDoc, removePunctuation)
        # Eliminate extra white spaces
        TextDoc <- tm_map(TextDoc, stripWhitespace)
        # Text stemming - which reduces words to their root form
        TextDoc <- tm_map(TextDoc, stemDocument)
        
        # Build a term-document matrix
        TextDoc_dtm <- TermDocumentMatrix(TextDoc)
        dtm_m <- as.matrix(TextDoc_dtm)
        # Sort by descearing value of frequency
        dtm_v <- sort(rowSums(dtm_m),decreasing=TRUE)
        dtm_d <- data.frame(word = names(dtm_v),freq=dtm_v)
        # Display the top 5 most frequent words
        set.seed(1234)
      
       # wordcloud2(data=dtm_d, size = 0.7, shape = 'pentagon')
        return(wordcloud(words = dtm_d$word, freq = dtm_d$freq, min.freq = 1,
          max.words=100, random.order=FALSE, rot.per=0.40, 
          colors=brewer.pal(8, "Dark2")))
        
})


```


Column {data-width=350}
-----------------------------------------------------------------------

### Emotions in Text

```{r}
plotOutput("emotions")
output$emotions <- renderPlot({
        
        # input$file1 will be NULL initially. After the user selects
        # and uploads a file, head of that data file by default,
        # or all rows if selected, will be shown.
        
        req(input$file1)
        
        text <- readLines(input$file1$datapath)
        # Load the data as a corpus
        TextDoc <- Corpus(VectorSource(text))
        
        #Replacing "/", "@" and "|" with space
        toSpace <- content_transformer(function (x , pattern ) gsub(pattern, " ", x))
        TextDoc <- tm_map(TextDoc, toSpace, "/")
        TextDoc <- tm_map(TextDoc, toSpace, "@")
        TextDoc <- tm_map(TextDoc, toSpace, "\\|")
        # Convert the text to lower case
        TextDoc <- tm_map(TextDoc, content_transformer(tolower))
        # Remove numbers
        TextDoc <- tm_map(TextDoc, removeNumbers)
        # Remove english common stopwords
        TextDoc <- tm_map(TextDoc, removeWords, stopwords("english"))
        # Remove your own stop word
        # specify your custom stopwords as a character vector
        TextDoc <- tm_map(TextDoc, removeWords, c("s", "company", "team")) 
        # Remove punctuations
        TextDoc <- tm_map(TextDoc, removePunctuation)
        # Eliminate extra white spaces
        TextDoc <- tm_map(TextDoc, stripWhitespace)
        # Text stemming - which reduces words to their root form
        TextDoc <- tm_map(TextDoc, stemDocument)
        
        # Build a term-document matrix
        TextDoc_dtm <- TermDocumentMatrix(TextDoc)
        dtm_m <- as.matrix(TextDoc_dtm)
        # Sort by descearing value of frequency
        dtm_v <- sort(rowSums(dtm_m),decreasing=TRUE)
        dtm_d <- data.frame(word = names(dtm_v),freq=dtm_v)
        syuzhet_vector <- get_sentiment(text, method="syuzhet")
# see the first row of the vector
head(syuzhet_vector)
# see summary statistics of the vector
summary(syuzhet_vector)
d<-get_nrc_sentiment(text)
# head(d,10) - to see top 10 lines of the get_nrc_sentiment dataframe
head(d,10)
td<-data.frame(t(d))
#The function rowSums computes column sums across rows for each level of a grouping variable.
td_new <- data.frame(rowSums(td))
#Transformation and cleaning
names(td_new)[1] <- "count"
td_new <- cbind("sentiment" = rownames(td_new), td_new)
rownames(td_new) <- NULL
td_new2<-td_new[1:8,]
        # Display the top 5 most frequent words
        
        return(barplot(sort(colSums(prop.table(d[, 1:8]))),horiz = TRUE, cex.names = 0.7,las = 1, main = "Emotions in Text", xlab="Percentage"))
})

#Plot two - count of words associated with each sentiment, expressed as a percentage

```

### Sentimental Analysis


```{r}
plotOutput("Sentiment")
output$Sentiment <- renderPlot({
        
        # input$file1 will be NULL initially. After the user selects
        # and uploads a file, head of that data file by default,
        # or all rows if selected, will be shown.
        
        req(input$file1)
        
        text <- readLines(input$file1$datapath)
        # Load the data as a corpus
        TextDoc <- Corpus(VectorSource(text))
        
        #Replacing "/", "@" and "|" with space
        toSpace <- content_transformer(function (x , pattern ) gsub(pattern, " ", x))
        TextDoc <- tm_map(TextDoc, toSpace, "/")
        TextDoc <- tm_map(TextDoc, toSpace, "@")
        TextDoc <- tm_map(TextDoc, toSpace, "\\|")
        # Convert the text to lower case
        TextDoc <- tm_map(TextDoc, content_transformer(tolower))
        # Remove numbers
        TextDoc <- tm_map(TextDoc, removeNumbers)
        # Remove english common stopwords
        TextDoc <- tm_map(TextDoc, removeWords, stopwords("english"))
        # Remove your own stop word
        # specify your custom stopwords as a character vector
        TextDoc <- tm_map(TextDoc, removeWords, c("s", "company", "team")) 
        # Remove punctuations
        TextDoc <- tm_map(TextDoc, removePunctuation)
        # Eliminate extra white spaces
        TextDoc <- tm_map(TextDoc, stripWhitespace)
        # Text stemming - which reduces words to their root form
        TextDoc <- tm_map(TextDoc, stemDocument)
        
        # Build a term-document matrix
        TextDoc_dtm <- TermDocumentMatrix(TextDoc)
        dtm_m <- as.matrix(TextDoc_dtm)
        # Sort by descearing value of frequency
        dtm_v <- sort(rowSums(dtm_m),decreasing=TRUE)
        dtm_d <- data.frame(word = names(dtm_v),freq=dtm_v)
        syuzhet_vector <- get_sentiment(text, method="syuzhet")
# see the first row of the vector
head(syuzhet_vector)
# see summary statistics of the vector
summary(syuzhet_vector)
d<-get_nrc_sentiment(text)
# head(d,10) - to see top 10 lines of the get_nrc_sentiment dataframe
head(d,10)
td<-data.frame(t(d))
#The function rowSums computes column sums across rows for each level of a grouping variable.
td_new <- data.frame(rowSums(td))
#Transformation and cleaning
names(td_new)[1] <- "count"
td_new <- cbind("sentiment" = rownames(td_new), td_new)
rownames(td_new) <- NULL
td_new2<-td_new[1:10,]
        # Display the top 5 most frequent words
        
        return(quickplot(sentiment, data=td_new2, weight=count, geom="bar", fill=sentiment, ylab="count")+ggtitle("Survey sentiments"))
})

#Plot One - count of words associated with each sentiment

```




WellBeing FlashCards
===============================

<center><h1>Tip Of The Day</h1></center>

Column {data-width=350}
-----------------------------------------------------------------------

```{r}


column(width = 4, offset = 4,
            valueBox(value= tags$img(height = 300, width = 300,src = "img1.jpg",style="display: block;
  margin-left: auto;
  margin-right: auto;"),icon="fa-user"))

```
Column {data-width=350}
-----------------------------------------------------------------------
Column {data-width=350}
-----------------------------------------------------------------------

```{r}

a<-"Establish regular exercise routines in your life."
b<-"Continue to work on eating healthily; vigilance will always be needed to be successful."
c<-"See your doctor regularly for wellness exams and health/disease screenings/tests."
d<-"If you have symptoms, seek medical attention."
e<-"Along with your body, make efforts to stimulate and strengthen your brain as you age."
f<-"Maintain satisfying social relationships."
g<-"Keep involved in activities and pursuits that interest you."
h<-"Try to maintain a positive attitude to support your resilience when life hands you setbacks."
i<-"Keep your body hydrated with water."
j<-"Take care of your skin."
k<-"Know your health numbers and what they mean, regardless of how healthy or unhealthy you are now."
l<-"Get adequate sleep."
m<-"Spend less time in front of the TV; at minimum, get up and move during commercials."
n<-"Learn to relax more."
o<-"Focus less on your weight, and more on your overall health."
p<-"Find things to be grateful for in your life."
q<-"Don’t forget to smile and laugh routinely."
r<-"Do something fun every day."
s<-"Have a sense of purpose in your life.Think about what is yours?"
t<-"Read Enemy Pie, a picture book which will teach you alot"


tips <- c(a,b,c,d,e,f,g,h,i,j,k,l,m,n,o,p,q,r,s,t)
num=round(runif(1)*20)
ans=tips[num]


column(width = 4, offset = 4,
            valueBox(value= tags$p(ans, style = "font-size: 200%;text-align:center;border-style: inset;border-color:white;"),icon="fa-user"))

```

Toxic People
=====================================================================

<h1>Toxic Person Check</h1>
Column {data-height=200}
----------------------------------------------------------------------

```{r}
  
textInput("toxicity", "Let's find out the impact of a person on your life")

```

Column {data-width=20}
----------------------------------------------------------------------

```{r}

UserInput <- reactive({c(input$toxicity)})

plotOutput('Toxic')
output$Toxic <- renderPlot({
  
      
        
        # input$file1 will be NULL initially. After the user selects
        # and uploads a file, head of that data file by default,
        # or all rows if selected, will be shown.
        
        req(input$file1)
        text <- readLines(input$file1$datapath)
        print(typeof(text))
        print(text)
        data=toString(text)
        print(data)
        data_split <- strsplit(data,"")[[1]];
data_lines<-c();
lines<-"";
for(i in data_split){
  if(i=='.'){
    lines<-paste(lines,i,sep="");
    data_lines<-append(data_lines,lines);
    lines<-''
  }else{
    lines<-paste(lines,i,sep="");
  }
}
print(data_lines)
special_lines<-c();

special_word <- UserInput()
print("HIIII")
print(special_word)
special_word <- toString(special_word)
#special_word <- "Ishita";

for(line in data_lines){
  words<-strsplit(line," ");
    if(grepl(special_word,words)){
      special_lines<-append(special_lines,line);
    }
}
print(special_lines);
        # Load the data as a corpus
        TextDoc <- Corpus(VectorSource(special_lines))
        
        #Replacing "/", "@" and "|" with space
        toSpace <- content_transformer(function (x , pattern ) gsub(pattern, " ", x))
        TextDoc <- tm_map(TextDoc, toSpace, "/")
        TextDoc <- tm_map(TextDoc, toSpace, "@")
        TextDoc <- tm_map(TextDoc, toSpace, "\\|")
        # Convert the text to lower case
        TextDoc <- tm_map(TextDoc, content_transformer(tolower))
        # Remove numbers
        TextDoc <- tm_map(TextDoc, removeNumbers)
        # Remove english common stopwords
        TextDoc <- tm_map(TextDoc, removeWords, stopwords("english"))
        # Remove your own stop word
        # specify your custom stopwords as a character vector
        TextDoc <- tm_map(TextDoc, removeWords, c("s", "company", "team")) 
        # Remove punctuations
        TextDoc <- tm_map(TextDoc, removePunctuation)
        # Eliminate extra white spaces
        TextDoc <- tm_map(TextDoc, stripWhitespace)
        # Text stemming - which reduces words to their root form
        TextDoc <- tm_map(TextDoc, stemDocument)
        
        # Build a term-document matrix
        TextDoc_dtm <- TermDocumentMatrix(TextDoc)
        dtm_m <- as.matrix(TextDoc_dtm)
        # Sort by descearing value of frequency
        dtm_v <- sort(rowSums(dtm_m),decreasing=TRUE)
        dtm_d <- data.frame(word = names(dtm_v),freq=dtm_v)
        
        syuzhet_vector <- get_sentiment(special_lines, method="syuzhet")
# see the first row of the vector
head(syuzhet_vector)
# see summary statistics of the vector
summary(syuzhet_vector)
d<-get_nrc_sentiment(special_lines)

# head(d,10) - to see top 10 lines of the get_nrc_sentiment dataframe
print(head(d,10))
td<-data.frame(t(d))
#The function rowSums computes column sums across rows for each level of a grouping variable.
td_new <- data.frame(rowSums(td))
C <- data.frame(rowSums(td))


#Transformation and cleaning
names(td_new)[1] <- "count"
td_new <- cbind("sentiment" = rownames(td_new), td_new)
rownames(td_new) <- NULL
td_new2<-td_new[9:10,]
        # Display the top 5 most frequent words
        
        return(quickplot(sentiment, data=td_new2, weight=count, geom="bar", fill=sentiment, ylab="count")+ggtitle("Survey sentiments"))
})

```

Export Your Diary On Your Whatsapp {data-width=350}
=====================================================================

<br><br><br><br><br>
<table border='0'>
<tr>
<td><h4>Enter Your Whatsapp Number To export the Data <br>(With your Country Codes eg : +91) :</td>

<td>
```{r}
textInput("contact", "", "")
```
</h4>
</td>
</tr>

<tr>
<td>
<h4>Enter Your Twilio Registered SID :</td>

<td>
```{r}
textInput("sid", "", "")
```
</h4>
</td>
</tr>

<tr>
<td>
<h4>Enter Your Twilio Registered Token ID :</td>
<td>

```{r}
textInput("token", "", "")
```

</h4>
</td>
</tr>
</table>

<center><b><h1 style="font-family: sans-serif;">Powered By Twilio</h1></b></center>

Column {data-width=20}
----------------------------------------------------------------------


```{r}
column(width = 4, offset = 4,
            valueBox(value= tags$img(height = 100, width = 100,src = "twilio.png",style="display: block;
  margin-left: auto;
  margin-right: auto;"),icon="fa-user"))

ContactInput <- reactive({c(input$contact)})
SidInput <- reactive({c(input$sid)})
TokenInput <- reactive({c(input$token)})

textOutput("export")

output$export <- renderText({
  library("twilio")
  req(input$file1)
  text <- readLines(input$file1$datapath)
  data=toString(text)
  
Sys.setenv(TWILIO_SID = toString(SidInput()))
Sys.setenv(TWILIO_TOKEN = toString(TokenInput()))

temp = 'whatsapp:'
temp2 = toString(ContactInput())

temp3 = paste(temp,temp2)
temp3=gsub(" ", "", temp3, fixed = TRUE)
print(temp3)
my_message <- tw_send_message(
 
  from='whatsapp:+14155238886',  
body=paste(data),      
to=temp3
)
p<- "Your Diary is Exported !! Check your Whatsapp."
  return(p)

}) 


```


